Aircraft Wildlife Collisions

### 2021-11-17 final_paper.Rmd
Rename files and add Readme

```{r echo=FALSE, fig.asp=0.5}
birds_strike_phase <- ggplot(birds[!is.na(birds$phase_of_flt) & !is.na(birds$birds_struck) & as.integer(birds$phase_of_flt)>2,]) +
  aes(x = phase_of_flt, fill=birds_struck) +
  scale_fill_brewer(palette="Blues") +
  geom_bar() +
  coord_flip() +
  theme.title+
  theme(legend.position="none",
        axis.title = element_text(vjust=-10),
        axis.title.y=element_blank(),
        axis.title.x=element_blank(),
        plot.subtitle = element_text(hjust =4)) +
  labs(xlab = "phase of flight",
       subtitle = "Number of collisions by phase of flight")

# Most collisions during the day #genauer betrachten
birds_strike_time <- ggplot(birds[!is.na(birds$time_of_day) & !is.na(birds$birds_struck),]) + 
  aes(x=time_of_day, fill=birds_struck) + 
  scale_fill_brewer(palette="Blues") +
  geom_bar() +
  coord_flip() +
  theme.title+
  theme(legend.position="none",
        axis.title.y=element_blank(),
        axis.title.x=element_blank(),
        plot.subtitle = element_text(hjust =3)) +
  labs(xlab = "",
       subtitle = "Number of collisions by time of day     ")

>>>>

```{r echo=FALSE, fig.asp=0.5}
birds_strike_phase <- ggplot(birds[!is.na(birds$phase_of_flt) & !is.na(birds$birds_struck) & as.integer(birds$phase_of_flt)>2,]) +
  aes(x = phase_of_flt, fill=birds_struck) +
  scale_fill_brewer(palette="Blues") +
  geom_bar() +
  coord_flip() +
  theme.title+
  theme(legend.position="none",
        axis.title = element_text(vjust=-10),
        axis.title.y=element_blank(),
        axis.title.x=element_blank(),
        plot.subtitle = element_text(hjust =2)) +
  labs(xlab = "phase of flight",
       subtitle = "Number of collisions by phase of flight")

# Most collisions during the day #genauer betrachten
birds_strike_time <- ggplot(birds[!is.na(birds$time_of_day) & !is.na(birds$birds_struck),]) + 
  aes(x=time_of_day, fill=birds_struck) + 
  scale_fill_brewer(palette="Blues") +
  geom_bar() +
  coord_flip() +
  theme.title+
  theme(legend.position="none",
        axis.title.y=element_blank(),
        axis.title.x=element_blank(),
        plot.subtitle = element_text(hjust =2)) +
  labs(xlab = "",
       subtitle = "Number of collisions by time of day     ")
